Approximating the Optimal State Abstraction

### 2016-05-01 icml_workshop/related_work.tex
added a bunch of rel work

Considerable work in planning and \ac{RL} has grappled with, either in the form of state aggregation (DEFINE?) or temporally extended actions (DEFINE?).

\subsection{Abstraction as State Aggregation}

\subsection{Approximate State Abstraction}

\citet{dean1997model} investigated partitioning an \ac{MDP}'s state space into $\varepsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\varepsilon$ of each other. They develop an algorithm called Interval Value Iteration (IVI) that converges to the correct bounds on a family of abstract MDPs called Bounded \acp{MDP}. Several approaches build on the notion of $\varepsilon$-homogeneity. \citet{even2003approximate} analyzed different distance metrics used in the process of identifying $\varepsilon$-homogenous partitions. \citet{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $\mcT$ and $\mcR$ provided by UCRL~\cite{auer2009near}.

@@

Many previous works have targeted the creation of algorithms that enable state abstraction for MDPs. \citet{andre2002state} investigated a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction. Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstractions that maintain optimality.

\citet{dietterich2000hierarchical} developed MAXQ, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied. \citet{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away in a factored-state \ac{MDP}.

For a more complete survey of algorithms that leverage state aggregation in past reinforcement-learning papers, see \citet{li2006towards}.

\subsection{Exact Abstraction Framework}

@@

\subsection{Abstraction as Temporal Extension}
Previous \textit{macro-action} or \textit{options}

\subsection{Abstraction as Function Approximation}

>>>>

Considerable work in planning and \ac{RL} has investigated abstraction. We group prior literature into approaches of state aggregation, temporally extended actions, or function approximation.

% Subsection: Abstraction as State Aggregation
\subsection{Abstraction as State Aggregation}

\citet{dean1997model} investigated partitioning an \ac{MDP}'s state space into $\varepsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\varepsilon$ of each other. They develop an algorithm called Interval Value Iteration (IVI) that converges to the correct bounds on a family of abstract MDPs called Bounded \acp{MDP}. Several approaches build on the notion of $\varepsilon$-homogeneity. \citet{even2003approximate} analyzed different distance metrics used in the process of identifying $\varepsilon$-homogenous partitions. \citet{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $\mcT$ and $\mcR$ provided by UCRL~\cite{auer2009near}. \citet{andre2002state} investigated a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction. Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstractions that maintain optimality. \citet{dietterich2000hierarchical} developed MAXQ, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied. \citet{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away in a factored-state \ac{MDP}. For a more complete survey of literature on state aggregation, see \citet{li2006towards}.

@@

% Subsection: Abs as Temp Ext.
\subsection{Temporal Abstraction}
Previous \textit{macro-action} or \textit{options}

% Subsection: Abstraction as Func Approx
\subsection{Abstraction as Function Approximation}

% Subsection: Exact Abstraction Framework
\subsection{Exact Abstraction Framework}

@@
